\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-01-12 AffineLieAlgebras/InformalNotes/article.tex
Coloring discarded.

(In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. {\color{red}(This is for us!)})
\begin{figure}[ph]
\noindent  \centering{
  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
  \end{array}
\end{equation}
{\color{blue} Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.}

{\color{blue} Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams. When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots  
$\Delta_{\bot}=\left\{\alpha\in \Delta:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ and correspondingly the positive roots
$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$. }

Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-module 
{\color{red} What is $\mathfrak{h}$? If it is the Cartan of $\mathfrak{g}$ then there are too many Cartans! It must be $\mathfrak{h}_{\mathfrak{a}}$.}
with the highest weight $\mu$. For the character of this module we have
\begin{equation}
  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
\end{equation}
The projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ gives us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

Using this property we can reconsider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
{\color{red}(This term is non-zero.) --This is for us.}
{\color{blue}Taking into account that for any formal series $Q \in {\cal E}$ and the binomial the projection commutes with the multiplication,
\begin{equation}
  \label{eq:6}
  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right),
\end{equation}
we can rewrite the 
product of (\ref{eq:4}) and (\ref{eq:5}) in the form:}
\begin{multline}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{multline}
The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}, by introducing the anomalous branching coefficients $k_{\lambda}$,
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}
and simplifying the multiplier:
\begin{multline}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{multline}

If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
{\color{red} (We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$) we are well acquainted with this!}
Let us reorganise the summation in the left-hand side of (\ref{eq:12}).
Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that 
{\color{red} $\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$. This is a mistake. Such a transformation may not exist. We can only insist on } $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
\begin{multline}
  \label{eq:13}
 \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
 \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
\end{multline}
The fraction in the right-hand side of the equation is similar to the character of some  $\mathfrak{a}_{\bot}$-module.
Let us rewrite the shifted weights
\begin{equation}
  \label{eq:30}
  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
\end{equation}

Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we get
\begin{multline}
  \label{eq:14}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{multline}
The projector $\pi_{\mathfrak{a}}$ transforms the character of the module ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into an element equal to the dimension of the module multiplied by the unit element {\color{red}" of the algebra of formal exponents" (for us)}:
  \begin{multline}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{multline}
{\color{red} These dimensions of the modules could be easily calculated using the Weyl formula. (for us)}

@@

{\color{red}(If the set $\Delta_{\bot}^{+}$ is empty the modules $L_{\mathfrak{a}_{\bot}}$ are trivial, the dimensions are equal to 1 and we get the following formula (11) \eqref{eq:40} from the paper \cite{ilyin812pbc}) This is not true! And the formula presented is not the one that was thus generalized.} 
{\color{blue} Now let the set $\Delta_{\bot}^{+}$ be empty. There are three different reasons for $\Delta_{\bot}^{+}=0$: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$. Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra: 
$\mathfrak{a}_{\bot}=0$. In any of these cases instead of the formal characters in the right-hand side of (\ref{eq:13}) we obtain the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$
In the first two cases (equivalent to $\mathfrak{a}_{\bot}=0$) the projection operator retains its purely geometrical meaning: the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$. It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra 
$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty we get the more simple recurrent relation: 
\begin{equation}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation special}
\end{equation}
It coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)). }

@@

The algorithm contains the following steps.
\begin{enumerate}
\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item {\color{red}"Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$."
 for  lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$. The same mistake!} Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
\end{enumerate}

>>>>

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. 
\begin{figure}[ph]
\noindent  \centering{
  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
  \end{array}
\end{equation}
Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.

Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams. When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots  
$\Delta_{\bot}=\left\{\alpha\in \Delta:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ and correspondingly the positive roots
$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$.

Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$-module 
with the highest weight $\mu$. For the character of this module we have
\begin{equation}
  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
\end{equation}
The projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ gives us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

Using this property we can reconsider the restriction $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, that is the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
Taking into account that for any formal series $Q \in {\cal E}$ and the binomial the projection commutes with the multiplication,
\begin{equation}
  \label{eq:6}
  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right),
\end{equation}
we can rewrite the 
product of (\ref{eq:4}) and (\ref{eq:5}) in the form:
\begin{multline}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{multline}
The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}, by introducing the anomalous branching coefficients $k_{\lambda}$,
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}
and simplifying the multiplier:
\begin{multline}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{multline}

If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
Let us reorganise the summation in the left-hand side of (\ref{eq:12}).
Consider the factor-space $W_{\bot}\backslash W$. For the class $\tilde{\omega}\in W_{\bot}\backslash W$ choose the representative $\omega \in \tilde{\omega}$ such that $\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)\in \bar{C}_{\mathfrak{a}_{\bot}}$,
\begin{multline}
  \label{eq:13}
 \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
 \pi_{\mathfrak{a}}\left(\sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right)
\end{multline}
The fraction in the right-hand side of the equation is similar to the character of some  $\mathfrak{a}_{\bot}$-module.
Let us rewrite the shifted weights
\begin{equation}
  \label{eq:30}
  \nu\cdot\omega(\mu+\rho)-\rho=\nu\cdot \bigl(\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}}+\pi_{\mathfrak{a}}(\omega(\mu+\rho))\bigr)-\rho
\end{equation}

Since $\nu\cdot \pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}}(\omega(\mu+\rho))$ and $\omega(\mu+\rho)-\pi_{\mathfrak{a}}(\omega(\mu+\rho))=\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))$, we get
\begin{multline}
  \label{eq:14}
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) \frac{\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot \omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}} =\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho} \frac{e^{\rho_{\mathfrak{a}_{\bot}} }\sum_{\nu\in W_{\bot}}\epsilon(\nu) e^{\nu \cdot (\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}=\\
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} {\rm ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}
\end{multline}
The projector $\pi_{\mathfrak{a}}$ transforms the character of the module ${\rm ch}L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$ into an element equal to the dimension of the module multiplied by the unit element:
  \begin{multline}
    \label{eq:15}
    \pi_{\mathfrak{a}}\left( \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho))-\rho}e^{\rho_{\mathfrak{a}_{\bot}}} \mathrm{ch} L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) = \\
    \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; \mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) e^{\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}
  \end{multline}

@@

Now let the set $\Delta_{\bot}^{+}$ be empty. There are three different reasons for $\Delta_{\bot}^{+}=0$: i) $\mathrm{dim}\mathfrak{h}_{\mathfrak{a}}=\mathrm{dim}\mathfrak{h}_{\mathfrak{g}}$, ii) $\mathfrak{a}_{\bot}=0$ and iii) $\mathfrak{a}_{\bot}\subset \mathfrak{h}_{\mathfrak{g}}$. Both the first and the second cases can be treated as corresponding to the trivial orthogonal subalgebra: 
$\mathfrak{a}_{\bot}=0$. In any of these cases instead of the formal characters in the right-hand side of (\ref{eq:13}) we obtain the formal element $e^{ \pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)}$
In the first two cases (equivalent to $\mathfrak{a}_{\bot}=0$) the projection operator retains its purely geometrical meaning: the vector $\omega(\mu+\rho)$ is projected to the subspace orthogonal to the weight space of $\mathfrak{a}$. It is clear that in any of the three variants the final vector $\pi_{\mathfrak{a}}\pi_{\mathfrak{a}_{\bot}}\omega(\mu+\rho)$ leads to the unit of the formal algebra 
$\mathcal{E}$. Thus when the set $\Delta_{\bot}^{+}$ is empty we get the more simple recurrent relation: 
\begin{equation}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
\left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)   \label{recurrent relation special}
\end{equation}
It coinsides with the one obtained in \cite{ilyin812pbc} (formula (16)).

@@

The algorithm contains the following steps.
\begin{enumerate}
\item Construct the sets $\Delta^{+}$ and $\Delta_{\mathfrak{a}}^{+}$ of positive roots for the algebras $\mathfrak{a} \subset \mathfrak{g}$.
\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous weights of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select the weights $\left\{ \lambda=\omega(\mu+\rho) | \pi_{\mathfrak{a}_{\bot}}\lambda \in \bar{C}_{\mathfrak{a}_{\bot}} \right\}$ Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check wether the weight $\pi_{\mathfrak{a}_{\bot}}\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ by computing the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ that must be non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \pi_{\mathfrak{a}_{\bot}}\lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate the anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
\end{enumerate}
